Story Cloze task -- XXX System

### 2017-02-03 docs/shared_task_paper.tex
Roy V3 (not final)

\begin{document}
\maketitle
\begin{abstract} % This is my real quick try at this lol
This paper describes our system for the Linking Models of Lexical, Sentential and Discourse-level Semantics (LSDSem 2017) shared task -- the \textit{Story Cloze Task}.
%
Our system feeds a linear classifier with a variety of features, including both the output of a neural language model and style features. %determine which of two endings best completes a short story.
We report  $75.2\%$ accuracy on the task.
\end{abstract}

@@

\subsection{Features}
We use two types of features, designed to capture different aspects of the problem. 
We use \textit{neural language model} features to leverage corpus level word distributions, specifically longer term sequence probabilities.
We use \textit{stylistic} features to capture differences in writing between ``coherent'' story endings and ``incoherent'' ones.

@@

The intuition is that a \emph{correct} ending should be unsurprising (to the model) given the four preceding sentences of the story (the numerator), controlling for the inherent surprise of the words in that ending (the denominator). 
We use these three probabilities as classification features.

@@

We train the RNNLM using a single-layer LSTM of hidden dimension 512.
We use the ROC Stories for training, setting aside 10\% for validation of the language model. 
We replace all words occurring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of 21,582.
Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. 
Using AdamOptimizer \cite{kingma2014adam} and a learning rate of
$\eta=.001$, we train to minimize cross-entropy.

For computing the style features, we keep n-gram (character or word) features that occur at least five times in the training set.
All stylistic feature values are normalized to [0-1].
For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
Our end system makes use of 7,651 distinct features.

>>>>

\begin{document}
\maketitle
\begin{abstract} % This is my real quick try at this lol
This paper describes our system for the Linking Models of Lexical, Sentential and Discourse-level Semantics (LSDSem 2017) shared task -- the \textit{Story Cloze Task}.
Our system feeds a linear classifier with a variety of features, including both the output of a neural language model and style features.
We report  $75.2\%$ accuracy on the task.
\end{abstract}

@@

\subsection{Features}
We use two types of features, designed to capture different aspects of the problem. 
We use \textit{neural language model} features to leverage corpus level word distributions, specifically longer term sequence probabilities.
We use \textit{stylistic} features to capture differences in writing between {\it coherent} story endings and {\it incoherent} ones.

@@

The intuition is that a \emph{correct} ending should be unsurprising (to the model) given the four preceding sentences of the story (the numerator), controlling for the inherent surprise of the words in that ending (the denominator). 
%We use these three probabilities as classification features.

@@

We train the RNNLM using a single-layer LSTM of hidden dimension 512.
We use the ROC Stories for training, setting aside 10\% for validation of the language model.\footnote{We train on both the Spring 2016 and the Winter 2017 datasets, a total of roughly 100K stories}
We replace all words occurring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of 21,582.
Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. 
Using AdamOptimizer \cite{kingma2014adam} and a learning rate of
$\eta=.001$, we train to minimize cross-entropy.

For computing the style features, we keep n-gram (character or word) features that occur at least five times in the training set.
All stylistic feature values are normalized to [0-1].
For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
The total number of features used by our system is 7,651.
